\documentstyle[bezier,12pt]{article}
\pagestyle{empty} 

\thicklines
\setlength{\unitlength}{1.2pt}
\input{rd7}
%
% Page Parameters (multiplied by 1.2 for 12pt---works better than magstep1)
%
\oddsidemargin 0in \evensidemargin 0in \topmargin 0.75in
\columnsep 10pt \columnseprule 0pt 
\marginparwidth 90pt \marginparsep 11pt \marginparpush 5pt 
\ignore{ 
 \topmargin 27pt \headheight 12pt \headsep 25pt \footskip 30pt 
  \textheight = 43\baselineskip
  \advance\textheight by \topskip
  \textwidth 345pt \columnsep 10pt \columnseprule 0pt 
}
\headheight 0pt \headsep 0pt 
\footheight 0pt \footskip 0pt 
\textheight 8in \textwidth 6.55in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\begin{document}

\ignore{	%%%%%%% <<<<<
  \setlength{\unitlength}{2pt}
  \thicklines
  \vspace{1in}
  \begin{center}

  \begin{picture}(140,85)
  \put(1,1){\framebox(138,83){}}
  \put(3,67){\framebox(134,15)[l]{\huge\bf\sl \raisebox{-4pt}{\llogo}\hfill ab/sp\ }}
  %\put(3,67){\framebox(134,15)[l]{\huge\bf\sl\ rd\seven\hfill ab/sp\ }}
  \put(3,3){\framebox(134,62){\logo}}
  \end{picture}

  \copyright\ 1988 by Silvermine Resources, Inc.
  All rights reserved.

  \end{center}
  \newpage
} 		%%%%%%% >>>>

\section*{{\sl Introducing: \RD}} 
{\sl NOW}, with \RD,
\begin{quote}
	you can
\end{quote}
Copy Perkin-Elmer 7000 Idris data to DOS using your PC
\begin{quote}
	Easily\\
	Quickly\\
	Conveniently\\
	Without tying up your instrument computer!
\end{quote}
 
The two versions of \RD, Version \AB\ for Ascii or Binary data and
Version \SP\ for Ascii, Binary, or Spectral data, are powerful, easy-to-use
PC/MS-DOS utilities which allow an IBM PC or compatible clone to
directly read and transfer data from 5 1/4 inch floppy disks written
by Perkin-Elmer's 7000 series Professional Data Stations under the
Idris operating system.  The utilities display the directories on the
7000 disk in tree form and, in an adjacent window, the contents of
each individual directory or subdirectory as it is selected in the
directory window.  Individual files can be viewed in either Ascii or
Binary form before transfer.  Files can be transferred individually or
files and/or whole directories can be ``tagged'' and, with a single
keystroke, written to any DOS disk or selected directory for further
processing by programs such as spreadsheets or databases.
 
In addition, \RD\ Version \SP\ recognizes spectral data in
Perkin-Elmer's .SP file format.  Viewing one of these files produces
a graphical display of the spectrum and a status report similar to
that produced by the Perkin-Elmer STATUS command.  Spectrum files can
be copied directly, transferred in JCAMP-DX format, or converted to
Perkin-Elmer's new Data Manager format for DOS based computers.
 
Lotus-like menu structure and extensive on-line context-sensitive
help make \RD\ particularly easy to use.  The user can also
display and examine DOS directories and files, to determine where
best to transfer files.  DOS files can also be viewed and copied
between disks or directories.
 
The \RD\ utilities are especially useful for examination and transfer of
data without involving the Perkin-Elmer computer which, in most
laboratories, tends to be busy with instrument oriented tasks.
 
\newpage
 
\section*{{\sl \RD\ Features}}
 
\begin{itemize}
 
\item
Works on any PC/MS-DOS computer, such as IBM PC/XT/AT or compatible
clones, and PS/2 systems fitted with 5 1/4 inch drives.
 
\item
Frees your PE7000 for instrument work.
 
\item
Work with PE7000 disks wherever your DOS Personal Computer is
located.
 
\item
Single-line menus with a second explanation line for each highlighted
selection guide the new or infrequent user.
 
\item
Single keystroke selection of menu items for the expert.
 
\item
Context-sensitive on-line help is provided, with a help screen for 
each menu; a manual is provided but is hardly necessary.
 
\item
Any 5 1/4 inch drive can be selected for input from the PE7000 disk.
 
\item
Any drive and/or directory can be selected for output to DOS; the
default is the current directory.
 
\item
Displays, at all times, the input drive, output drive, and output
directory path.
 
\item
Displays, in tree form, either the Idris or the DOS directory
structure.
 
\item
Displays, in list form, the files in any selected DOS
directory, including date last modified and size in bytes.
 
\item
Displays, in list form, the files in any selected Idris
directory, including date last modified, size in bytes, and transfer
option.
 
\item
Displays the contents of any selected file on either Idris or DOS in
either ASCII or Binary (Hexadecimal plus ASCII) format; allows
scrolling by line or page.
 
\item
Version \SP---View of .SP files displays the spectrum and full status
report from the spectrum header, including instrument number, date
and time written, and IDENT line.
 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\newpage
% Following needs work, particularly expansion of your bio.
% Put into a page in TEX form for the brochure.  My plan is to have
% page 1 = Introducing, page 2 = some screen shots, page 3 =
% specifications, and page 4 = the following with lower right of page
% having address(PO Box) and phone no.



\begin{center}
{\sl About Silvermine Resources and \RD}
\end{center}

Dr. Abraham Savitzky, President and Director of Software Development,
formed Silvermine Resources following his retirement from The
Perkin-Elmer Corporation.  He was a pioneer in the use of computers in
analytical chemistry.\cite{as1,as2} At Perkin-Elmer he had been
responsible for the development of all the spectroscopy data handling
products from the earliest time sharing software, through the
Interdata 6/16 minicomputer, through the 3500/3600 Data Station CDS
software, and finally the CDS III software for the 7000 series Data
Station.  He wrote the data transfer modules for transfer of 3500/3600
data to CDS III.  He was Perkin-Elmer's representative on the JCAMP
committee which developed the Data Exchange
Specifications.\cite{JCAMP} As a consultant to Perkin-Elmer he wrote
the current CDS III JCAMP conversion routines TODX and FRDX.  \RD\ was
written to answer his personal needs for access to 7000 files on
Personal Computers.

Coauthor Stephen Savitzky, who studied at the Artificial Intelligence
Laboratory of Stanford University, has had extensive experience
writing microcomputer software.  He is the author of the book, {\em
Real-Time Microprocessor Systems},\cite{ss1} assemblers and linkers
for Zilog's entire line of microprocessors, a real-time operating
system kernel for the Zilog Z8000, and several debuggers and text
editors.  He served on the IEEE standards committees for
microprocessor assembly language\cite{IEEE-694} and object-file
formats.\cite{IEEE-695}

%%% Local version of thebibliography
%%% so we can change the heading to a simple rule
%%%
\def\thebibliography#1{\medskip
\noindent\ \hrulefill\ 
\medskip\list
 {[\arabic{enumi}]}{\settowidth\labelwidth{[#1]}\leftmargin\labelwidth
 \advance\leftmargin\labelsep
 \usecounter{enumi}}
 \def\newblock{\hskip .11em plus .33em minus .07em}
 \sloppy\clubpenalty4000\widowpenalty4000
 \sfcode`\.=1000\relax}

{\small
\begin{thebibliography}{9}
\bibitem{as1}
	Savitzky, A., ``Data Processing in Analytical Chemistry'',
	Analytical Chemistry (33), 25A, December 1961.
\bibitem{as2}
	Savitzky, A. and Golay, M.J.E., ``Smoothing and Differentiation
	of Data by Simplified Least Squares Procedures'', Analytical
	Chemistry (36) 1627, July 1964.
\bibitem{JCAMP}
	McDonald, R.S. and Wilks,P.A., ``JCAMP-DX: A Standard Form for
	Exchange of Infrared Spectra in Computer Readable Form'', 
	Applied Spectroscopy (42) 151, January 1988.
\bibitem{ss1}
	Savitzky, S., {\em Real-Time Microprocessor Systems},
	Van Nostrand Reinhold, New York, 1985.
\bibitem{IEEE-694}
	ANSI/IEEE Standard 694-1985, {\em Microprocessor
	Assembly Language}.
\bibitem{IEEE-695}
	IEEE Trial Use Standard 695-1985, {\em Microprocesor Universal
	Format for Object Modules}.
\end{thebibliography}
}
\medskip
\noindent\ \hrulefill\ 
\begin{center}
	Silvermine Resources, Inc.	\\
	P.O. Box 7474			\\
	Wilton, CT 06897		\\
	(203)762-1155			\\
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\newpage
\begin{center}
     LIMITED USE SOFTWARE LICENSE AGREEMENT AND LIMITED WARRANTY
\end{center}

Silvermine Resources, Inc. appreciates your selection of this product.
We value our customers and respect your needs.  This card contains
the limited use software license and limited warrenty.  By opening
the sealed disk package, you accept the terms of the license and of
the warranty.  If you do not agree with these terms, you may return
this product, with the disk package unopened, for a full refund.

LICENSE:  rd7 Version AB or rd7 Version SP:  This software and manual
are protected by United States Copyright Law and International Treaty
provisions.  Any unauthorized use, distribution, or modification,
including (but not limited to) disassembly or patching of the
program, is a violation of Federal law.  You may copy this software for
purposes of backup, for use on working disks, or to a hard disk.
However, you may use this product only on a single CPU and a single
keyboard.  Timely return of the enclosed registration card is a 
condition of this license.  

ACCEPTANCE:  By opening the sealed disk package and using this
software you agree to the above terms and will actively discourage use
of this software other than authorized above, and will report any
unauthorized use immediately.

LIMITED WARRANTY:  Silvermine Resources, Inc. warrants the diskette
and related printed material to be free from defects in materials and
workmanship in their intended use and service for a period of 90 days
from the effective day of this agreement.  If, during the 90 day period
a defect appears, you may return the defective material for
replacement without charge, PROVIDED you have returned your
registration card.  Silvermine Resources, Inc. makes no other
warranties, expressed or implied.  In particular the buyer assumes
all risk regarding any incidental or consequential damages resulting
from any defect in the licensed software.  

\sloppypar
EXCEPT FOR THE WARRANTY DESCRIBED IN THE ABOVE PARAGRAPH, THERE ARE
NO WARRANTIES EXPRESSED OR IMPLIED, INCLUDING BUT NOT LIMITED TO,
IMPLIED WARRANTIES OF MERCHANT\-ABILITY OR FITNESS FOR A PAR\-TIC\-U\-LAR
PURPOSE, AND ALL SUCH WARRANTIES ARE EXPRESSLY AND SPECIFICALLY
DISCLAIMED.  IN NO EVENT SHALL SILVERMINE RESOURCES, INC. BE LIABLE
FOR ANY LOSS OF PROFIT OR ANY OTHER COMMERCIAL DAMAGE, INCLUDING BUT
NOT LIMITED TO SPECIAL, INCIDENTAL, CONSEQUENTIAL OR OTHER DAMAGES.

\bigskip
\noindent\ \hrulefill\ 
\bigskip
\begin{center}
	Silvermine Resources, Inc.	\\
	P.O. Box 7474			\\
	Wilton, CT 06897		\\
	(203)762-1155			\\
\end{center}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\newpage

\begin{center}
                               ORDER FORM
\end{center}

Terms and Conditions:
\begin{itemize}
\item 
  rd7AB and rd7SP are licenced for use on a single CPU and 
	with a single keyboard.

\item
 All orders must be prepaid in US Dollars drawn on a US bank
	or by International Money Order.

\item
 In the continental US, orders are shipped by United Parcels,
	prepaid. 

\item 
 In Connecticut, add $7\frac{1}{2}\%$ Sales Tax.
\end{itemize}

\begin{tabbing}
\hspace{2.75in} \= To:  \= \+\+ \\
	Silvermine Resources, Inc.	\\
	P.O. Box 7474			\\
	Wilton, CT 06897		\\
\end{tabbing}
\newcommand{\blankline}{\rule[-0.5pt]{3in}{0.5pt}}
\begin{tabbing}
SHIP TO: \= Company:  \=  \kill
SHIP TO: \+ \\
	Name:    \> \blankline \\
        Title:   \> \blankline \\
	Company: \> \blankline \\
	Address: \> \blankline \\
		 \> \blankline \\
		 \> \blankline \\
		 \> \blankline \\
	Phone:   \> \blankline \\
\end{tabbing}

\newcommand{\leftc}{\multicolumn{1}{|c|}{}}
 
\begin{tabular}{|c|l|c|c|}
\hline
Quantity & \multicolumn{1}{|c|}{ITEM}		& Price Each 	& Amount \\
\hline
\hline
\leftc	& rd7 Version AB                   	& \$275.00	&	\\
\hline
\leftc	& rd7 Version SP                   	& \$450.00	&	\\
\hline
\leftc	& Upgrade Version AB to Version SP 	& \$250.00	&	\\
\leftc	& \hspace{1em}Furnish Serial Numbers of	&		&	\\
\leftc	& \hspace{1em}each Version AB upgraded.	&		&	\\
\hline
								\cline{4-4}
	\multicolumn{3}{r|}{SUBTOTAL\ } 			&	\\
								\cline{4-4}
	\multicolumn{3}{r|}{Shipping\ }				&	\\
								\cline{4-4}
	\multicolumn{3}{r|}{$7\frac{1}{2}\%$ CT Sales Tax\ }	&	\\
								\cline{4-4}
	\multicolumn{3}{r|}{TOTAL\ }				&	\\
								\cline{4-4}
\end{tabular}

\medskip
\newcommand{\checkoff}{\rule[-0.5pt]{1em}{0.5pt}}
Payment enclosed:   Check \checkoff\ International Money Order \checkoff.

\medskip 
rd7AB and rd7SP \copyright\ Copyright 1988, Silvermine Resources, Inc.
 
\end{document}
 
 
 
 
