\documentstyle[bezier]{article}
\pagestyle{empty} 

\thicklines
\setlength{\unitlength}{1pt}
\input{rd7}
%
% Page Parameters
%
\oddsidemargin 0in \evensidemargin 0in \topmargin 0.75in
\columnsep 10pt \columnseprule 0pt 
\marginparwidth 90pt \marginparsep 11pt \marginparpush 5pt 
\ignore{ 
 \topmargin 27pt \headheight 12pt \headsep 25pt \footskip 30pt 
  \textheight = 43\baselineskip
  \advance\textheight by \topskip
  \textwidth 345pt \columnsep 10pt \columnseprule 0pt 
}
\headheight 0pt \headsep 0pt 
\footheight 0pt \footskip 0pt 
\textheight 8in \textwidth 5in
\parindent 0pt  \parskip 4pt

%
% Useful rules
%
\newcommand{\threepica}{\rule{0.3in}{0.5pt}}
\newcommand{\oneinch}{\rule{1in}{0.5pt}}
\newcommand{\twoinch}{\rule{2in}{0.5pt}}
\newcommand{\restofline}{\hrulefill}
%\newcommand{\restofline}{\rule[-0.5pt]{1\fill}{0.5pt}}

%
% 2inch right column column
%
\newcommand{\rightcol}[1]{\makebox[2in]{#1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\begin{document}
To receive technical support and update information you must return
this card.  Fill out completely, fold, seal, and mail.
\begin{center}
Registration and License/Warranty Agreement     
\end{center}

\sloppypar
EXCEPT FOR THE WARRANTY DESCRIBED IN THE ENCLOSED LICENSE AND
WARRANTY, THERE ARE NO REPRESENTATIONS NOR WARRANTIES EXPRESSED OR
IMPLIED, INCLUDING BUT NOT LIMITED TO, IMPLIED WARRANTIES OF
MERCHANT\-ABILITY OR FITNESS FOR A PAR\-TIC\-U\-LAR PURPOSE, AND ALL
SUCH WARRANTIES ARE EXPRESSLY AND SPECIFICALLY DISCLAIMED.  IN NO
EVENT SHALL SILVERMINE RESOURCES, INC.  BE LIABLE FOR ANY LOSS OF
PROFIT OR ANY OTHER COMMERCIAL DAMAGE, INCLUDING BUT NOT LIMITED TO
SPECIAL, INCIDENTAL, CONSEQUENTIAL OR OTHER DAMAGES.

\bigskip

\RD\ \ Version\oneinch\ Serial No.\restofline

\bigskip

The Limited Use Software License Agreement and Limited Warranty
provided with this software is confirmed.

\medskip
Signature\twoinch\hfill Date\twoinch

\begin{center}
Please Print:
\end{center}



Name\restofline			\rightcol{Phone No.(\threepica)\restofline}

Company\restofline

Address\restofline

City\restofline 		\rightcol{State\threepica Zip\restofline}

PE Instrument(s) in use\restofline

7000 Software in use\restofline

\medskip
Additional information about your PC:

\medskip
Computer Brand\restofline 	\rightcol{Model\restofline}

Operating System\restofline 	\rightcol{Hard Disk?(Y/N)\restofline}

Graphics Card\restofline 	\rightcol{Monitor Type\restofline}

How did you learn about this program?\restofline

Comments\restofline

\mbox{}\restofline














\ignore{
\bigskip
\noindent\ \hrulefill\ 
\bigskip
\begin{center}
	Silvermine Resources, Inc.	\\
	P.O. Box 7474			\\
	Wilton, CT 06897		\\
	(203)762-1155			\\
\end{center}
}

\end{document}
 
 
 
 
